%-------------------------
% CV in Latex
% Author : Reza Ghanbari Amoughin
% Website: https://github.com/rezaghanbari/cv
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://rezaghanbari.github.io/}{\Large Reza Ghanbari Amoughin}} & Email : \href{mailto:ghanbari.reza94@gmail.com}{ghanbari.reza94@gmail.com}\\
  \href{https://rezaghanbari.github.io/}{https://rezaghanbari.github.io} & Mobile : +98-912-830-1806 \\
  {No. 51, Aseman Tower, 9th Nassim, Kouhak, Tehran}\\
  Links:
  \href{https://scholar.google.com/citations?user=DsVeq5UAAAAJ&hl=en}{\small{Google scholar}}, 
  \href{https://www.researchgate.net/profile/Reza_Ghanbari9}{\small{Researchgate}},
   \href{https://www.linkedin.com/in/rezaghanbari/}{\small{Linkedin}}
  \end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kharazmi University of Tehran}{Tehran, Iran}
      {Master of Science in Computer Science;  GPA: 3.15}{Sep. 2017 -- Sep. 2020}
    \textit{\small{Received full scholarship from Kharazmi University of Tehran (tuition waiver)}}\\
\textit{\small{The best thesis among students of the faculty of Computer Science in 2020 }}\\
\-
    \resumeSubheading
      {Amirkabir University of Technology(Tehran Polytechnic)}{Tehran, Iran}
      {Bachelor of Science in Computer Science}{Sep. 2012 -- July. 2017}
    \textit{\small{Received full scholarship from Amirkabir University of Tehran (tuition waiver)}}

  \resumeSubHeadingListEnd

%-----------Research Interest----------
\section{Research Interest}
{\small {Deep Learning, Distributed Systems, Data Intensive Computing, Data Mining, Self-Adaptive Systems}\\


%-----------Publications---------------
\section{Publications}
\begin{itemize}
	\item Journals
	\begin{itemize}
	\item {\textit {K. Borna, R.Ghanbari, Hierarchical LSTM network for text classification, SN Applied Sciences (Springer International Publishing), Vol 1, Issue 9, 2019}}\\
	\item {\textit {R. Ghanbari, K. Borna, S. Arabi, A Self-Adaptive Deep Learning Model to Predict Cloud Workload, The Journal of Supercomputing (Submitted)}}\\
	\item {\textit{R. Ghanbari, K. Borna, Improve the Raft consensus algorithm using deep learning, IEEE Transactions on Industrial Informatics (In Prep)}}\\
	\end{itemize}
	
	\item Proceedings
	\begin{itemize}
	\item {\textit {K. Borna, R.Ghanbari, On a Novel Algorithm for Digital Resource Recommender Systems, International Congress on High-Performance Computing and Big Data Analysis (Springer, Cham), Pages 418-425, 2019}}\\
	\end{itemize}
	\end{itemize}


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Cloud Manager}
      {Analysis of a self-adaptive deep learning based system to reduce the use of cloud resources and improve processing rates.}
    \resumeSubItem{Captcha Breaker}
      {Enhanced a system to bypass Google's captcha v3 system using automated tools and image detection algorithms.}
    \resumeSubItem{ISP API Gateway}
      {Developed an intelligent API-gateway written in Golang, in order to maintain the ISP CRM requests with automatic rollback and failure detection including audit logs and admin panel.}
    \resumeSubItem{Dublin QLindex}
      {Created a system for determining the quality of life index in Dublin using deep learning algorithms and tools like Tensorflow, Kafka, Python and Google Cloud.}
    \resumeSubItem{Twitter Sentiment Analysis}
      {Sentiment analysis using Python on Farsi tweets; furthermore developed a specific library for natural language processing in Farsi.}
    \resumeSubItem{Ride-Hailing}
      {Created a ride-hailing system based on macro-service architecture using Golang, MongoDB, Cassandra, Elastic Search and MQTT.}
    \resumeSubItem{Geo-Map}
      {Created a local map and geo-fencing system for urban transport services with a very fast cache system.}
    \resumeSubItem{Nginx Modules}
      {Developed Nginx modules using Lua programming language to manage requests (Canary release, request-response transformer, REST to SOAP and custom logger).}
    \resumeSubItem{Prediction as a Service}
      {Predicting stocks markets using machine learning algorithms.}
    \resumeSubItem{Customizing Gitlab}
      {Developed a custom authentication and authorization system for Gitlab CE.}
  \resumeSubHeadingListEnd


%-----------Seminars and Workshops-----
\section{Seminars and Workshops}
\begin{itemize}
	\item {\textit {High Performance Computing and Big Data Analytics, Hotel Espinas Palace, 23-25 April 2019, Tehran, Iran }}
	\item {\textit {CEIT-SSC Docker and Kubernetes workshop, Amirkabir University of Technology, Jan 2017, Tehran, Iran }}
	\item {\textit {Network Plus workshop, Amirkabir University of Technology, Dec 2015, Tehran, Iran }}\end{itemize}

%-----------Awards and Honors----------
\section{Awards and Honors}
\begin{itemize}
  \item {\textit{The first 0.5 percent of those admitted to the entrance exam of the country's universities}}
  \item {\textit{Top positions in artificial intelligence programming competitions in the undergraduate}}
  \item {\textit{Top positions in the high school programming competitions (ACM)}}
\end{itemize}

%-----------EXPERIENCE-----------------
\section{Experience\\}
\-

\textbf{Teaching Experience}

\resumeSubHeadingListStart
	
    \resumeSubheading
      {Teacher Assistant}{Tehran, Iran}
      {Amirkabir University of Technology}{ }
      \resumeItemListStart
        \resumeItem{Database} {Sep 2015 - Feb 2016}
        \resumeItem{Topics in Computer Science	(Web Programming)} {Jan 2015 - Jul 2015}
 		\resumeItem{Computer Networks} {Jan 2015 - Jul 2015}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\noindent\rule{8cm}{0.4pt}\\\-



\textbf{Industry Experience}
  \resumeSubHeadingListStart
	
    \resumeSubheading
      {Farda Studio}{Tehran, Iran}
      {Technical Team Lead}{Apr 2019 - Present}
      \resumeItemListStart
        \resumeItem{Apieco}
          {I am responsible for the development of cloud-native applications, using Golang and Ruby On Rails; moreover, the creation of high-tech and distributed solutions to manage the cloud workload would be a major part of this role.}\\\-
   
      \resumeItemListEnd

    \resumeSubheading
      {QLindex}{Dublin, Ireland}
      {Senior Software Engineer}{Sep 2019 - Mar 2020}
      \resumeItemListStart
        \resumeItem{Qlindex MVP}
          {I was responsible for designing and developing an urban service system in Dublin so that we could use novel software tools to provide an integrated service which facilitates utilising public transportation and measuring the quality of life. These services include accurate transportation information, weather conditions, crime rates and quality of life in different parts of the city.}\\\-
      \resumeItemListEnd
      
      \resumeSubheading
      {Carpino, Ride-Hailing Application}{Tehran, Iran}
      {Technical Team Lead}{Mar 2018 - Apr 2019}
      \resumeItemListStart
        \resumeItem{Carpino App}
          {As a team-lead I was responsible for the stack migrations. We have migrated the legacy stack written in Java 8 into Golang with the help of 15 micro-services.}\\\-
      \resumeItemListEnd
      
      \resumeSubheading
      {Hamitrip}{Tehran, Iran}
      {Software Engineer}{Aug 2017 - Mar 2018}
      \resumeItemListStart
        \resumeItem{Tour App}
          {Developed tour and travel reservation systems using Python, Kafka and Cassandra database.}
        \resumeItem{Captcha Pass}
          {Created an intelligent system written in Python to bypass simple-captcha using Tensorflow and RNN algorithms.}\\\-
      \resumeItemListEnd
      
      
      \resumeSubheading
      {Nullatech}{Tehran, Iran}
      {Software Engineer and Co-founder}{Dec 2016 - Dec 2017}
      \resumeItemListStart
        \resumeItem{Nullatech App}
          {Predicting stocks markets using machine learning algorithms.}\\\-
      \resumeItemListEnd
      
      
      \resumeSubheading
      {APZSharif}{Tehran, Iran}
      {Software Engineer}{Sep 2015 - Sep 2016}
      \resumeItemListStart
        \resumeItem{Jabir Hayyan System}
          {Created a comprehensive system for connecting the community of researchers and manufacturers of medical materials for the Ministry of Health of Iran.}\\\-
      \resumeItemListEnd


		\resumeSubheading
      {Smartleo}{Milan, Italy}
      {Software Engineer}{Oct 2014 - Sep 2015}
      \resumeItemListStart
        \resumeItem{Smartleo price comparison app}
          {Enhanced a horizontal search engine for price comparison.}\\\-
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
 \item{\textbf{Languages}{: TOEFL (to be taken 10 October)}}
   \item{\textbf{Programming Languages}{: Golang, Python, C++, Rust, Lua, Julia}}
   \item{\textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Cassandra, Redis}}
   \item{\textbf{Technologies}{: Kubernetes, Docker, Tensorflow, PyTorch, AWS, GCP, Django, Ruby On Rails, Kafka, Nginx, Git}}
 \resumeSubHeadingListEnd

%-------Memberships and Activities---------
\section{Memberships and Activities}
 \resumeSubHeadingListStart
   \item{\textit{IEEE Transactions on Industrial Informatics, Journal reviewer, Since 2020}}
   \item{\textit{The Journal of Super Computing, Journal reviewer, Since 2020}}
   \item{\textit{Python Software Foundation, Community Member, Since 2015}}
   \item{\textit{Cloud Native Computing Foundation, Community Member, Since 2019}}
   \item{\textit{Bayan 3rd Programming Contest, Technical Staff, 2015}} 
   \item{\textit{TEDxAUT - Digging Deep, Staff, 2016}} 
 \resumeSubHeadingListEnd
 
 %-------Hobbies---------
\section{Hobbies}
 \resumeSubHeadingListStart
   \item{\textbf{Track and Field (several championships in the province and the country), Swimming (safe guard)}}
 \resumeSubHeadingListEnd


%--------References------
\section{References}
\begin{itemize}
	\item
	Dr. Keivan Borna\\
		Assistant Professor, Department of Computer Science, Master's thesis supervisor\\
	\href{mailto:borna@khu.ac.ir}{borna@khu.ac.ir}\\
	 {\href{https://khu.ac.ir/cv/209/keivan-borna?slc_lang=en&&cv=209&mod=scv}{\small{https://khu.ac.ir/cv/209/keivan-borna}}}\\\-

\item
	Dr. Somayeh Arabi\\
		Assistant Professor, Department of Computer Science, Master's thesis supervisor\\
	\href{mailto:somaye.arabi@gmail.com}{somaye.arabi@gmail.com}\\
	 {\href{https://khu.ac.ir/cv/223/Somayeh-Arabi?slc_lang=en&&cv=223&mod=scv}{\small{https://khu.ac.ir/cv/223/Somayeh-Arabi}}}\\\-
	 
\item
	Dr. Adel Mohammadpour\\
		Associate Professor, Department of Mathematics and Computer Science, Bachelor's thesis supervisor\\
	\href{mailto:adel@aut.ac.ir}{adel@aut.ac.ir}\\
	 {\href{https://aut.ac.ir/cv/2026/Adel\%20Mohammadpour}{\small{https://aut.ac.ir/cv/2026/Adel\%20Mohammadpour}}}\\\-
	 
\item
	Dr. Fatemeh Zare Mirakabad\\
		Assistant Professor, Department of Mathematics and Computer Science, Bachelor's consultant professor\\
	\href{mailto:f.zare@aut.ac.ir}{f.zare@aut.ac.ir}\\
	 {\href{https://aut.ac.ir/cv/2148/Fatemeh\%20Zare\%20Mirakabad}{\small{https://aut.ac.ir/cv/2148/Fatemeh\%20Zare\%20Mirakabad}}}\\\-
	
\end{itemize}
%-------------------------------------------

\end{document}